Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-26 manuscript/manuscript.Rmd
another fig caption

```{r knit_global, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
library(tidyverse)
library(patchwork)
```

@@

```{r timeseries, fig.cap="TBD.", out.width = "6.5in"}
policy_labels <- list("msy" = "MSY Const. Mortality", "tac"= "80% MSY Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 6) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```

>>>>

```{r knit_global, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, 
                      warning = FALSE, fig.height=5, fig.width=7.5)
library(tidyverse)
library(patchwork)
```

@@

```{r} 
#| label: timeseries 
#| fig.cap: "A sample time series for the three fish populations, with the system being controlled, respectively, by the MSY optimal mortality, by $80$ percent of the MSY optimal mortality, and by DRL." 
#| out.width: "6.5in"
policy_labels <- list("msy" = "MSY Const. Mortality", "tac"= "80% MSY Const. Mortality", "ppo"= "DRL")
policy_labeller <- function(variable,value){
  return(policy_labels[value])
}
msy_tac_ppo |> 
    group_by(rep, policy) |>
    filter(rep == 6) |>
    ggplot(aes(t, abundance, col = species)) + 
        geom_line()  + 
        scale_color_manual(values=c('palegreen3', 'coral1', 'deepskyblue4')) +
        facet_wrap(~factor(policy, levels = c("msy", "tac", "ppo")), labeller = policy_labeller ) +
        labs(y = "abundance", x = "time") +
        theme(aspect.ratio = 2/3)
```
